The LSST-DESC 3x2pt Tomography Optimization Challenge

### 2021-06-24 paper/paper.tex
typo

\section{Normalized metric scores} \label{app:metric_grids}
Figures \ref{fig:metric_grid_dc2_riz}, \ref{fig:metric_grid_buzzard_griz}, and \ref{fig:metric_grid_buzzard_riz} show metric scores normalized bewteen random assignment and perfect assignemtn to equal number density bins for CosmoDC2/riz, Buzzard/griz and Buzzard/riz respectively

>>>>

\section{Normalized metric scores} \label{app:metric_grids}
Figures \ref{fig:metric_grid_dc2_riz}, \ref{fig:metric_grid_buzzard_griz}, and \ref{fig:metric_grid_buzzard_riz} show metric scores normalized bewteen random assignment and perfect assigment to equal number density bins for CosmoDC2/riz, Buzzard/griz and Buzzard/riz respectively
